### 2015-10-03 untitled.tex
edited untitled.tex

In this section, we demonstrate with an example that there exist sets of segmented self-suspending sporadic tasks that both \textbf{(i)} are schedulable \emph{without} period enforcement and \textbf{(ii)} are not schedulable under the period enforcer.

@@

\section{How to Convert to the Corresponding Deferrable Task Set}
\label{sec:convert}

>>>>

In this section, we demonstrate with an example that there exist sporadic  segmented self-suspending task sets that both \textbf{(i)} are schedulable \emph{without} period enforcement and \textbf{(ii)} are not schedulable under the period enforcer.

@@

\section{How to Derive the Corresponding Deferrable Task Set}
\label{sec:convert}
